Mining sequential mobility patterns from semantic Twitter user trajectories

### 2016-04-19 sq_mobility/sq_mobility_twitter.tex
add

\section*{Introduction}
Understanding detailed human mobility patterns is great importance for

>>>>

\section*{Introduction}
Understanding detailed human mobility patterns in the urban settings is critical for a wide range applications, such as urban planning, traffic management, and even the spatial spread of disease.
